True versus apparent shapes of astrophysical bow shocks

### 2017-04-05 papers/Paper1/sec-quadrics-observations.tex
Add the plot with 5-sample partitioning on H0

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
  \caption{Box plots of the distributions of bow shock shape
    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), as a function of bow
    shock size, \(R_0\).  All 3-, 4-, and 5-star sources are sorted
    according to \(R_0\) and divided into 5 non-overlapping
    sub-samples of roughly equal size, each labelled by their median
    value of \(R_0\) in arcseconds, as illustrated in the lower panel.
    The colored boxes show the interquartile range, with the median
    indicated by a horizontal line, the 1st-to-9th interdecile range
    by error bars, and outliers by diamonds.  It is apparent that the
    dispersion in \(R_{90} / R_0\) (upper panel) increases
    systematically with \(R_0\), although the central value is roughly
    constant.  No clear systematic changes are apparent in
    \(R_c / R_{90}\) (middle panel).}
  \label{fig:mipsgal-boxplot}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics[height=0.8\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
    & \includegraphics[height=0.8\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-H0}
  \end{tabular}
  \caption{(a) Box plots of the distributions of bow shock shape
    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), after partitioning
    on the bow shock size, \(R_0\).  All 3-, 4-, and 5-star sources
    are sorted according to \(R_0\) and divided into 5 non-overlapping
    sub-samples of roughly equal size, each labelled by their median
    value of \(R_0\) in arcseconds, as illustrated in the lower panel.
    The colored boxes show the interquartile range, with the median
    indicated by a horizontal line, the 1st-to-9th interdecile range
    by error bars, and outliers by diamonds.  It is apparent that the
    dispersion in \(R_{90} / R_0\) (upper panel) increases
    systematically with \(R_0\), although the central value is roughly
    constant.  No clear systematic changes are apparent in
    \(R_c / R_{90}\) (middle panel).  (b)~As (a), but partitioning on
    the extinction-corrected \(H\)-band magnitude, \(H_0\).  Note that
    sub-samples are plotted in order of \textit{decreasing} magnitude
    to allow comparison between (a) and (b), given the negative
    correlation between \(H_0\) and \(R_0\) (see
    Fig.~\ref{fig:mipsgal-pairplot}).}
  \label{fig:mipsgal-boxplot}
\end{figure}
